Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-09-21 gnd_dn_lambda.tex
[review] Forgot to commit just now. Fig. 3, 4, 5, 11 changed. Appendices are rearranged such that analytical ones are before the numerical ones.

In this appendix, we calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}. In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and conformal interface $\lambda$ at $x = 0$. The general solutions can be written as
\begin{equation}
\label{eq:normalized_f}
f(k, x) = 
\left\lbrace
\begin{aligned}
  A_1 e^{i kt} \cos\left(kx +\frac{1}{2}kL \right) &  \quad x < 0  \\
  A_2 e^{ikt}  \sin\left(kx - \frac{1}{2}kL \right) & \quad x > 0 .  \\
\end{aligned} \right. 
\end{equation}
As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction becomes
\begin{eqnarray}\begin{aligned}
\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2}, \quad \theta \in \left[0,\frac{\pi}{2} \right]  ,
\end{aligned}\end{eqnarray}
which implies
\begin{equation}
\label{eq:momentum_gnd_dn_lambda}
k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right),  \quad n\in\mathbb{Z}.
\end{equation}
It is evident that the momentum $k$ is shifted from integer multiple of $\frac{2\pi}{L}$ due to the $\lambda$ boundary condition in the middle.

>>>>

In this appendix, we calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}. In particular, the unfolded configuration has D/N boundary conditions at $y = \pm \frac{L}{2}$ and conformal interface $\lambda$ at $y = 0$. The general solutions can be written as
\begin{equation}
\label{eq:normalized_f}
f(k, y) = 
\left\lbrace
\begin{aligned}
  A_1 e^{i kt} \cos\left(ky +\frac{1}{2}kL \right) &  \quad y < 0  \\
  A_2 e^{ikt}  \sin\left(ky - \frac{1}{2}kL \right) & \quad y > 0 .  \\
\end{aligned} \right. 
\end{equation}
As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,y<0)\equiv\phi_1$ and $f(k,y>0)\equiv\phi_2$, the boundary condition at the junction becomes
\begin{eqnarray}\begin{aligned}
\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2}, \quad \theta \in \left[0,\frac{\pi}{2} \right]  ,
\end{aligned}\end{eqnarray}
which implies
\begin{equation}
\label{eq:momentum_gnd_dn_lambda}
k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right),  \quad n\in\mathbb{Z}.
\end{equation}
It is evident that the momentum $k$ is shifted from integer multiple of $\frac{2\pi}{L}$ due to the $\lambda$ boundary condition in the middle.

### 2017-09-21 num_result.tex
[review] Forgot to commit just now. Fig. 3, 4, 5, 11 changed. Appendices are rearranged such that analytical ones are before the numerical ones.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$. We work with the total system size $N = 30$k sites, and parameters $m = 10^{-8}$, $k = 1$. The lattice constant is set to unity. The blue dots representing the numerical results lie on the red analytic line. As predicted, the echo exponents are all equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale. The dashline denotes the expected power law of $t^{-0.25}$. Finite size effect does not emerge before $t=10^{3}$, which sets the right boundary of the range we fit. See main text for the curve fitting method.}
\label{fig:DDDD}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35$k sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$. We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$. The lattice constant is set to unity. The blue dots representing the numerical results lie on the red analytic line. As predicted, the echo exponents are all equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale. The dashline denotes the expected power law of $t^{-0.25}$. Finite size effect does not emerge before $t=10^{3}$, which sets the right boundary of the range we fit. See main text for the curve fitting method.}
\label{fig:DDDD}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}
